\documentclass[9.5pt,a4paper]{article}


% ---------- Packages ----------
\usepackage{lmodern}
\usepackage[margin=0.4in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}


% ---------- Formatting ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\linespread{1.0}


\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{7pt}{6pt}


\setlist[itemize]{
  noitemsep,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=*
}


% ---------- Document ----------
\begin{document}


% ---------- Header ----------
\begin{center}
    {\LARGE \textbf{Jack Butlin}} \\[6pt]
    UK Citizen \\[6pt]
    Cybersecurity, Cloud Computing, App Development \\[6pt]  
    \href{mailto:jackashleyb@icloud.com}{jackashleyb@icloud.com} \,|\, 
    \href{https://github.com/jackashleyb}{github.com/jackashleyb}
\end{center}

 % ---------- Education ----------
\section*{Education}
\textbf{BSc Cybersecurity} \hfill \textit{Graduating 2028 } \\
University of West London, United Kingdom
\begin{itemize}
    \item Grade: On track for a First Class Honors. 
    \item Modules: Algorithms and Data Types, Mathematics for Computing, Object Oriented Programming, Cloud Computing.
\end{itemize}

% ---------- Projects ----------
\section*{Projects}

\textbf{IOS App Development - Learn Cloud, Study for Cloud Computing Certifications} \\
\textit{Swift, SwiftUI, GitHub, Apple Developer, ChatGPT, ChatGPT Codex, Full Stack Development}
\begin{itemize}
    \item Designed, developed and deployed a cloud computing education iOS app using SwiftUI and SwiftData
    \item aimed at helping users prepare for cloud certifications, devlope their cloud skills and track their learning progress.
    \item Features include vendor-neutral learning modules, certification-specific quiz banks, a study streak mechanic.
\end{itemize}

\textbf{Simple Long Short Equity Strategy In Python} \\
\textit{Python, Pandas, NumPy, yFinance}
\begin{itemize}
    \item Implements a hypothesis of going long on underperforming stocks while also maintaining a short position on stocks within the same sector that are overperforming.
    \item Backtested and on 5 years of historical data. Using historical market data for Google, Meta, S\&P 500 and Microsoft.
    \item Version-controlled project with Git and is published on a GitHub: \href{https://github.com/jackashleyb/simple-long-short-equity-strategy-in-python}{Repository}.
\end{itemize}


\textbf{Simple Moving Average (SMA) Crossover Trading Strategy} \\
\textit{Python, yFinance, Pandas, Matplotlib, GitHub}
\begin{itemize}
    \item Built a Python trading strategy using short-term and long-term moving average crossovers.
    \item Processed and analyzed historical prices with Pandas and yFinance; visualized trends and signals using Matplotlib.
    \item Version-controlled project with Git and is published on a GitHub: \href{https://github.com/jackashleyb/Simple-Moving-Average-SMA-Crossover-Trading-Strategy}{Repository}.
\end{itemize}

% ---------- Certifications ----------
\section*{Certifications}
\begin{itemize}
    \item AWS Cloud Practitioner – Going through online training including AWS skills builder and AWS online labs in preparation for this exam this quarter.
    \item AWS Emerging Talent Community Member - active member of this program that gives me access to online labs and extra development in cloud principles.
    \item CompTIA Cloud Essentials - Online fundamentals training that gives an overview of cloud essentials.
    \item CompTIA AI Fundamentals - Online fundamentals that gives me an overview of ai prompting and how to prompt effectively and effienclty.
    \item AWS Educate Getting Started With Security (Online Lab) - AWS online labs that demonstrates hands on work with aws systems.
\end{itemize}

% ---------- Skills ----------
\section*{Skills}
\begin{tabular}{@{}l l@{}}
\textbf{Programming Language:} & Python, Swift, SwiftUI \\
\textbf{Web Technologies:} & HTML, CSS, Flask \\
\textbf{Cloud \& DevOps:} & AWS (EC2, S3, IAM), Git, GitHub, Version Control \\
\textbf{Tools:} & VS Code, GitHub, Xcode with Agentic Workflows, ChatGPT, ChatGPT Codex \\
\end{tabular}

% ---------- Experience ----------
\section*{Experience}
\textbf{University Coursework and Labs}
\begin{itemize}
    \item \textbf{Algorithm \& Data Structures Project:} Implemented stacks, queues, linked lists, recursion, sorting, and searching algorithms in Python
    \item \textbf{Quantitative Trading Mini-Project:} Developed Python scripts for automated trading strategies, including data analysis and chart output
\end{itemize}



% ---------- Interests ----------
\section*{Interests}
LaTeX, software development, cloud security, financial technology, learning new programming tools, and contributing to personal GitHub projects


\vspace*{6pt}
\end{document}
